What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments

### 2023-07-31 manuscript.Rmd
added to intro

```{=html}
<!-- MAJOR TO DOs: 
 - get data from in-lab versions of group A (AJ) and group D (RR)
 - replicate group D and A in lab

 (see bottom for notes from e-mails)
 -->
```
Intro stuff:

-   Eye-tracking as a key method in cognitive science research

-   Online data collection is more and more popular & let's us ask new
    questions, test more diverse populations

-   But, concerns over quality + little known about eye-tracking online

@@

```{r E1-analysis-replication, child = 'group-a/E1-analysis-replication.Rmd'}

@@

```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}

>>>>

The use of eye-tracking to study cognition took off when Alfred Yarbus used suction cups to affix a mirror system to the sclera of the eye in order to monitor eye position during the perception of images [@yarbus1967eye]. In one study, participants viewed a painting depicting multiple people in a complex interaction inside of a 19th century Russian home. Yarbus showed, among other things, that the scan paths and locations of fixations were largely dependent on the instructions given to participants (e.g., View the picture freely vs. Remember the position of the people and objects in the room). In other words, the cognitive processing that the individual is engaged in drives the visuo-motor system. Since these findings, eye-tracking has become a central method in cognitive science research [for reviews, see @hayhoe2005eye, @richardsonEyeTrackingResearch2004, @rayner1998eye]. For example, gaze location during natural scene perception is used to test theories of visual attention [e.g., @henderson2017meaning]. And eye-movements during auditory language comprehension demonstrated the context-dependent and incremental nature of language processing [e.g., @tanenhaus1995].

An important limitation of the eye-tracking methodology is that it has typically required costly equipment (eye-trackers can range in price from a few thousand dollars to tens of thousands of dollars), particular laboratory conditions (a quiet room with consistent indoor lighting conditions), and a substantial time investment (e.g., bringing participants into a laboratory one at a time). This limits who can conduct eye-tracking research -- not all researchers have the necessary resources -- and who can participate in eye-tracking research. Most eye-tracking study participants are from western, educated, industrialized, rich, and democratic [WEIRD; @henrich2010weirdest] convenience samples [but see @ryskin2023real], which diminishes the generalizability of the findings and the scope of conclusions that can be drawn about human cognition.

Advances in software for online data collection [@deleeuwJsPsychJavaScriptLibrary2015; @papoutsaki2016webgazer] have the potential to address this shortcoming by expanding access to eye-tracking technology for researchers and making it feasible to broaden and diversify the participant samples. In particular, Webgazer.js [@papoutsaki2016webgazer] is a webcam-based Javascript plug-in that works in the browser. It can be integrated with any Javascript web interface. As a result, it can be used in conjunction with many existing platforms for online behavioral data collection that are familiar to cognitive scientists, such as jsPsych [@deleeuwJsPsychJavaScriptLibrary2015], Gorilla [@anwyl2020gorilla], or lab.js [@henninger2021lab]. However, the added convenience comes at the cost of spatial and temporal resolution. The extent of this loss of precision and its impact on the kinds of research questions that webcam eye-tracking is appropriate for are not yet known.

A few previous studies have used webcam eye-tracking in the context of behavioral/cognitive science experiments and reported on the quality of the data. In what follows, we provide a brief review of the published work that we are aware of (note that we focus on studies with adult participants as the considerations for eye-tracking of children are substantially different, but see e.g., @banki2022comparing).

@semmelmann2018online compared eye-tracking results between in-lab and online studies in three tasks: fixation, pursuit, and free viewing.

Yang & Krajbich,

slim & hartsuiker

@@

```{r E1-analysis-replication,eval=FALSE, child = 'group-a/E1-analysis-replication.Rmd'}

@@

```{r E1-analysis-calibration,eval=FALSE, child = 'group-a/E1-analysis-calibration.Rmd'}
